SDR enhancement by clouds

### 2024-03-21 article/article.Rmd
Commit 2024-03-21 12:16
Commit 2024-03-21 13:31

Our monitoring site is operating in the Laboratory of Atmospheric Physics of the
Aristotle University of Thessaloniki (\(40^\circ\,38'\,\)N,
\(22^\circ\,57'\,\)E, \(80\,\)m\ a.s.l.).
In this study we present data from the period
`r strftime(min(ST_daily$Date), "%d\\ %B %Y")` to
`r strftime(max(ST_daily$Date), "%d\\ %B %Y")`.

<!-- Instrument -->
The GHI data were measured with a Kipp\ & Zonen CM-21 pyranometer.
During the study period, the pyranometer was independently calibrated three times at
the Meteorologisches Observatorium Lindenberg, DWD, verifying that the stability of
the instrument’s sensitivity was better than $0.7\%$ relative to the initial
calibration by the manufacturer.

<!-- Measurements -->
For the acquisition of radiometric data, the signal of the pyranometer was sampled
at a rate of $1\,\text{Hz}$.
The mean and the standard deviation of these samples were calculated and recorded
every minute.
The measurements were corrected for the zero offset ("dark signal" in volts), which
was calculated by averaging all measurements recorded for a period of $3\,\text{h}$,
before (morning) or after (evening) the Sun reaches an elevation angle of $-10^\circ$.
The signal was converted to irradiance using a ramped value of the instrument’s
sensitivity between subsequent calibrations.

<!-- Radiation data quality check -->
To further improve the quality of the irradiance data, a manual screening was
performed to remove inconsistent and erroneous recordings that can occur
stochastically or systematically during the continuous operation of the instruments.
The manual screening was aided by a radiation data quality assurance procedure,
adjusted for the site, which was based on the methods of Long and Shi\ [@Long2006; @Long2008a].
Thus, problematic recordings have been excluded from further processing.
Although it is impossible to detect all false data, the large number of available
data, and the aggregation scheme we used, ensures the quality of the radiation
measurements used in this study.

<!-- Data selection -->
To preserve an unbiased representation of the data we applied a constraint similar
the one used by @CastillejoCuberos2020. Where, for each valid hour of day, there
must exist at list 45 minutes of valid measurements, including nighttime near
sunrise and sunset. Days with less than 5 valid hours are rejected completely.
<!--# CastillejoCuberos2020 There must be at least 5 h of valid data (Tests 1–7),
otherwise all data for this day is flagged as invalid. There must be at least This
work valid data 45 min of valid data (Tests 1–7) for an hour to be flagged as valid,
otherwise all minute data for this hour is flagged as invalid. -->
Furthermore, due to the significant measurement uncertainty when the Sun is near the
horizon, and to some systematic obstructions by nearby buildings, we have excluded
all measurements with solar zenith angle (SZA) greater than $`r 90-BIO_ELEVA`^\circ$.

<!--
- available data
  - sky cam
  - chp1
  - cm21
  - cimel
- CSid tool
-->

@@

In order to identify CE cases, we need an approximation of the expected clear sky GHI
for the whole period of the study, with a temporal resolution of one minute.  Because
of the lack of exact data about atmospheric factors, responsible for the attenuation
of the solar radiation in the atmosphere, we can not recreate a minute by minute
representation of the reference radiation. Thus, we used some climatological data
with a radiation transfer model.

We decided to use the Libradtran [@Emde2016] radiation transfer model, to model
the clear sky equivalent of GHI, with monthly climatological data of AOD and water
column from the Aerosol Robotic Network (AERONET) [@Giles2019; @Buis1998].  Our site
participates in AERONET, where we operate a Cimel photometer, collocated to
the CM-21 pyranometer, since 2003

For the production of .....

We also used the Sun's total solar irradiance from NOAA [@Coddington2005] and the
Earth - Sun distance calculated by Astropy [@AstropyCollaboration2022].  We simulated
the clear sky radiation, using the solar radiation spectrum of @Kurucz1994 in the
range $280$ to $2500\,\text{nm}$, with a SZA step of $0.2^\circ$.  For the
atmospheric characteristics, we used combinations of AOD at $500\,\text{nm}$
($t_{500\text{nm}}$) and additional offsets of $\pm1$ and $\pm2\sigma$, water column
($w_h$) with offsets of $\pm1$ and $\pm2\sigma$, and applied it to two atmospheric
profiles "AFGL atmospheric constituent profile, midlatitude summer" (afglms) and
"AFGL atmospheric constituent profile, midlatitude winter" (afglmw) [@Anderson1986].
Thus, we were able to emulate different atmospheric condition and level of
atmospheric clearness for the climatological conditions of the site.

>>>>

The monitoring site is operating in the Laboratory of Atmospheric Physics of the
Aristotle University of Thessaloniki (\(40^\circ\,38'\,\)N,
\(22^\circ\,57'\,\)E, \(80\,\)m\ a.s.l.).
In this study we present data from the period
`r strftime(min(ST_daily$Date), "%d\\ %B %Y")` to
`r strftime(max(ST_daily$Date), "%d\\ %B %Y")`.
<!-- Instrument -->
The GHI data were measured with a Kipp\ & Zonen CM-21 pyranometer.  During the study
period, the pyranometer was independently calibrated three times at the
Meteorologisches Observatorium Lindenberg, DWD, verifying that the stability of the
instrument’s sensitivity was better than $0.7\%$ relative to the initial calibration
by the manufacturer.
<!-- Measurements -->
For the acquisition of radiometric data, the signal of the pyranometer was sampled at
a rate of $1\,\text{Hz}$.  The mean and the standard deviation of these samples were
calculated and recorded every minute.  The measurements were corrected for the zero
offset ("dark signal" in volts), which was calculated by averaging all measurements
recorded for a period of $3\,\text{h}$, before (morning) or after (evening) the Sun
reaches an elevation angle of $-10^\circ$.  The signal was converted to irradiance
using the ramped value of the instrument’s sensitivity between subsequent
calibrations.

<!-- Radiation data quality check -->
To further improve the quality of the irradiance data, a manual screening was
performed to remove inconsistent and erroneous recordings that can occur
stochastically or systematically during the continuous operation of the instruments.
The manual screening was aided by a radiation data quality assurance procedure,
adjusted for the site, which was based on the methods of Long and Shi\ [@Long2006;
@Long2008a].  Thus, problematic recordings have been excluded from further
processing.  Although it is impossible to detect all false data, the large number of
available data, and the aggregation scheme we used, ensures the quality of the
radiation measurements used in this study.
<!-- Data selection -->
To preserve an unbiased representation of the data we applied a constraint similar
the one used by @CastillejoCuberos2020. Where, for each valid hour of day, there
must exist at list 45 minutes of valid measurements, including nighttime near
sunrise and sunset. Days with less than 5 valid hours are rejected completely.
<!--# CastillejoCuberos2020 There must be at least 5 h of valid data (Tests 1–7),
otherwise all data for this day is flagged as invalid. There must be at least This
work valid data 45 min of valid data (Tests 1–7) for an hour to be flagged as valid,
otherwise all minute data for this hour is flagged as invalid. -->
Furthermore, due to the significant measurement uncertainty when the Sun is near the
horizon, and to some systematic obstructions by nearby buildings, we have excluded
all measurements with solar zenith angle (SZA) greater than $`r 90-BIO_ELEVA`^\circ$.

@@

In order to identify CE cases, we used a modeled approximation of the expected clear
sky GHI.  Because of the lack of observational data for the whole period, we used
some long term climatological data for the main factors responsible for the
attenuation of the broadband downward solar radiation in the atmosphere, which are
mainly the aerosols and the water vapors. Fortunately, our site participates in the
Aerosol Robotic Network (AERONET) [@Giles2019; @Buis1998], as we operate a Cimel
photometer since 2003, collocated with the CM-21 pyranometer.  The mean monthly
aerosol optical depth (AOD) on different wavelengths is provided by AERONET along
with the equivalent water column height in the atmosphere.  The simulation of the
clear sky radiation was performed by the well established radiation transfer model
Libradtran [@Emde2016].

For completeness we will describe the main points of the radiation simulation
procedure here.  We used as input the spectrum of @Kurucz1994 in the range $280$ to
$2500\,\text{nm}$.

We also used the Sun's total solar irradiance from NOAA [@Coddington2005] and the
Earth - Sun distance calculated by Astropy [@AstropyCollaboration2022].

We simulated
the clear sky radiation, using the solar radiation , with a SZA step of $0.2^\circ$.
For the
atmospheric characteristics, we used combinations of AOD at $500\,\text{nm}$
($t_{500\text{nm}}$) and additional offsets of $\pm1$ and $\pm2\sigma$, water column
($w_h$) with offsets of $\pm1$ and $\pm2\sigma$, and applied it to two atmospheric
profiles "AFGL atmospheric constituent profile, midlatitude summer" (afglms) and
"AFGL atmospheric constituent profile, midlatitude winter" (afglmw) [@Anderson1986].
Thus, we were able to emulate different atmospheric condition and level of
atmospheric clearness for the climatological conditions of the site.
